---
title: "HW 1"
author: "Xing Chen"
date: 2019-9-19
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```


#**Problem 1**

##create a data frame containing 4 variables

```{r}
set.seed(1)

problem1_df = tibble(
  sample = rnorm(8),
  sample_logic = sample > 0,
  sample_char = c("hellow", "world", "this", "this", "is", "a","test", "!"),
  sample_factor = factor(c("apple", "banana", "grape", "banana", "grape",
                           "apple", "grape", "apple"))
)

mean(pull(problem1_df, sample))

mean(pull(problem1_df, sample_logic))

mean(pull(problem1_df, sample_char))

mean(pull(problem1_df, sample_factor))
```

The mean value of variable sample and sample_logic can be calculated becuase the value stored in these 2 variables are numbers.

The mean value for variable sample_logic and sample_char cannot be calculated because the value  stored in these 2 variables are string. 

##coerce the variables to numeric

```{r, results='hide'}
as.numeric(pull(problem1_df, sample_logic))

as.numeric(pull(problem1_df, sample_char))

as.numeric(pull(problem1_df, sample_factor))
```

explainating...

##coerce the variables into different classes

```{r}
as.numeric(pull(problem1_df, sample_logic)) * pull(problem1_df, sample)

as.factor(pull(problem1_df, sample_logic)) * pull(problem1_df, sample)

as.numeric(as.factor(pull(problem1_df, sample_logic))) * pull(problem1_df, sample)
```

#Problem 2

#create a dataframe with 5 variables
```{r}
set.seed(10)

problem2_df = tibble(
  x = rnorm(500),
  y = rnorm(500),
  var_logic = x + y > 1,
  var_num = as.numeric(var_logic),
  var_factor = as.factor(var_logic)
)
```

 The data frame problem2_df has `r nrow(problem2_df)` rows and 
`r ncol(problem2_df)` columns. 
The mean value of x is `r mean(pull(problem2_df, x))`, the median value of x is `r median(pull(problem2_df, x))`, and the standard deviation of x is `r sd(pull(problem2_df, x))`. The proportion for `x + y > 1` is `r mean(pull(problem2_df, var_logic) == "TRUE")`

##plot 3 scatterplots for variables x and y, colored by different variables
```{r}
a = ggplot(problem2_df, aes(x = x, y = y, color = var_logic)) + geom_point()

b = ggplot(problem2_df, aes(x = x, y = y, color = var_num)) + geom_point()

c = ggplot(problem2_df, aes(x = x, y = y, color = var_factor)) + geom_point()

```

##comment on color scale
In both 3 plots, the color of the dots are devided into 2 colors. Because in logical vector, var_logic, only 2 values "true" and "false" can be found. The numeric variable, var_num, is converted from var_logic. Thus, only 0 and 1 are stored in this variable. In var_factor, the logical vector is converted to a categorical variable, containing the value "TRUE" and "FALSE". 

