---
title: "HW 1"
author: "Xing Chen"
date: 2019-9-19
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```


# **Problem 1**

## create a data frame containing 4 variables

```{r}
set.seed(1)

problem1_df = tibble(
  sample = rnorm(8),
  sample_logic = sample > 0,
  sample_char = c("hellow", "world", "this", "this", "is", "a","test", "!"),
  sample_factor = factor(c("apple", "banana", "grape", "banana", "grape",
                           "apple", "grape", "apple"))
)

mean(pull(problem1_df, sample))

mean(pull(problem1_df, sample_logic))

mean(pull(problem1_df, sample_char))

mean(pull(problem1_df, sample_factor))
```

The mean value of variable sample and sample_logic can be calculated becuase the value stored in these 2 variables are numbers.

The mean value for variable sample_logic and sample_char cannot be calculated because the value  stored in these 2 variables are string. 

## coerce the variables to numeric

```{r, results='hide'}
as.numeric(pull(problem1_df, sample_logic))

as.numeric(pull(problem1_df, sample_char))

as.numeric(pull(problem1_df, sample_factor))
```

The logical vector is successful coerced to numeric because within R, the value "TRUE" is stored as 1 and value "FALSE" is stored as 0 and therefore it can be converted into numeric form. 

The character vector is not successfully coerced to numeric because a string cannot be converted into numeric form. 

The factor vector is successfully coerced to numeric eventhough the value in this vector is string. This is because the level concept in factor. The level of each value is shown when "as.numeric" is applied to a factor vector. 

I think this partly expalin what happens when I take the mean of each vaector. The one that can be succeffully coerced by "as.numeric" can be applied to a mean calculation. However, a factor can be coerced by "as.numeric" but still cannot be applied to a mean calculation. 

## coerce the variables into different classes

```{r}
as.numeric(pull(problem1_df, sample_logic)) * pull(problem1_df, sample)

as.factor(pull(problem1_df, sample_logic)) * pull(problem1_df, sample)

as.numeric(as.factor(pull(problem1_df, sample_logic))) * pull(problem1_df, sample)
```


# Problem 2

# create a dataframe with 5 variables
```{r}
set.seed(10)

problem2_df = tibble(
  x = rnorm(500),
  y = rnorm(500),
  var_logic = x + y > 1,
  var_num = as.numeric(var_logic),
  var_factor = as.factor(var_logic)
)
```

 The data frame problem2_df has `r nrow(problem2_df)` rows and 
`r ncol(problem2_df)` columns. 
The mean value of x is `r mean(pull(problem2_df, x))`, the median value of x is `r median(pull(problem2_df, x))`, and the standard deviation of x is `r sd(pull(problem2_df, x))`. The proportion for `x + y > 1` is `r mean(pull(problem2_df, var_logic) == "TRUE")`

## plot 3 scatterplots for variables x and y, colored by different variables
```{r}
ggplot(problem2_df, aes(x = x, y = y, color = var_logic)) + geom_point()

ggplot(problem2_df, aes(x = x, y = y, color = var_num)) + geom_point()

ggplot(problem2_df, aes(x = x, y = y, color = var_factor)) + geom_point()
```

## comment on color scale
When the plot is colored by logical vector, two colors are created for the value "TURE" and"FALSE". 

When the plot is colored by numeric variable, a series of colors, ranged from light to dark, are created. But this numeric variable is converted from a logical variable. Thus only two values exist in it and the dots are only in 2 colors.

When the plot is colored by factor variable, the number of colors are created depending on the level of factor variable. Because this factor variable is converted from a logical variable, only 2 levels exist in it and the dots in the scatter plot are in 2 colors.

## output the first plot
```{r}
ggsave("scatter_plot.pdf", plot = ggplot(problem2_df, aes(x = x, y = y, color = var_logic)) + geom_point())
```
