---
title: "HW 1"
author: "Xing Chen"
date: 2019-9-19
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```


#**Problem 1**

##create a data frame containing 4 variables

```{r}
set.seed(1)

problem1_df = tibble(
  sample = rnorm(8),
  sample_logic = sample > 0,
  sample_char = c("hellow", "world", "this", "this", "is", "a","test", "!"),
  sample_factor = factor(c("apple", "banana", "grape", "banana", "grape",
                           "apple", "grape", "apple"))
)

mean(pull(problem1_df, sample))

mean(pull(problem1_df, sample_logic))

mean(pull(problem1_df, sample_char))

mean(pull(problem1_df, sample_factor))
```

The mean value of variable sample and sample_logic can be calculated becuase the value stored in these 2 variables are numbers.

The mean value for variable sample_logic and sample_char cannot be calculated because the value  stored in these 2 variables are string. 

##coerce the variables to numeric

```{r, results='hide'}
as.numeric(pull(problem1_df, sample_logic))

as.numeric(pull(problem1_df, sample_char))

as.numeric(pull(problem1_df, sample_factor))
```

explainating...

##coerce the variables into different classes

```{r}
as.numeric(pull(problem1_df, sample_logic)) * pull(problem1_df, sample)

as.factor(pull(problem1_df, sample_logic)) * pull(problem1_df, sample)

as.numeric(as.factor(pull(problem1_df, sample_logic))) * pull(problem1_df, sample)
```




